---
title: "R Project 1 - Hello R"
author: "Merveilles Mvoula"
date: "1/23/2020"
output: 
  html_document: 
    fig_height: 6
    highlight: zenburn
    theme: cosmo
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

number of rows = 13
number of columns = 2


### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=6, fig.width=8}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:
```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The r value from the dino is less than the r value from the star.

### Exercise 4

First let's plot the data in the circle dataset:

```{r plot-circle, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
```{r cor-circle}
star_data %>%
  summarize(r = cor(x, y))
```
r circle is less than r dino

### Exercise 5

First let's plot all the datasets
(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)
```{r plot-all the datasets}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

And next calculate their summary correlation coefficients between `x` and `y` in this dataset:
```{r cor-summary}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

